\chapter*{Conclusions and Future Work}
\label{cap:conclusions}
\addcontentsline{toc}{chapter}{Conclusions and Future Work}

Conclusions and future lines of work. This chapter contains the translation of Chapter \ref{cap:conclusiones}.

Taking into account the entire process, the development of VitHabitus has been a technical and a rewarding challenge, as it was my first step into the world of mobile applications.

In the end, most of the initial objectives were successfully achieved, including the development of both the frontend and backend, the implementation of the API and the integration with Firebase as the database. The habit recommendation algorithm was also successfully incorporated, resulting in a coherent and functional flow between all components.

The final product is an application that can be highly useful for many users and it clearly showcases the incredible potential of artificial intelligence when applied to health. Also, it demonstrates how mobile app development can serve as an effective channel for bringing complex technologies into people's everyday lives, thanks to an intuitive and easy-to-use interface accessible from any smartphone

\subsection*{Future Work}

Regardless of the current outcome, there is always room for improvement and growth.
Some ideas emerged throughout the development process and some of the mos relevant are this ones:
\begin{itemize}
    \item Implement connectivity with wearable devices equipped with sensors that could track valuable data such as heart rate, sleep duration, calories burned... variables that could been applied to the recommendation system.
    \item Officially publish the app on Google Play and Apple Store, which involve setting the required standards and ensuring continuous updates.
    \item Translating the app into multiple languages, or at least into English, to increase its potential to reach the international market.
    \item In the visual aspects, improving some aspects of the user interface to achieve more polished and visual finish.
\end{itemize}

